saycam bb outputs compile

### 2021-04-16 preprocessing/_old/4_preprocess_datasets.Rmd
reorganize preprocessing folder -- port old scripts to old folder

## Load, process, merge Y's data
### Now load in bounding box data from Y, which has detection rates built in
```{r}
load('../data/Y_bounding_boxes.RData') #df again as import
y_data <- df %>%
  rowwise() %>%
  mutate(age = str_split_fixed(vid_name, '_',4)[,3])
remove(df)

@@

## frame
# height_px = 480; width_px = 640
# bb_all_three <- d_y %>%
#   filter(person==0) %>% # only rows with detections for now so comparable to bb_all
#   mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data so comparable
#   full_join(bb_all) %>% # join with SA bounding boxes
#   mutate(center_x = left + width/2, center_y = top - height/2, area = width*height) 
# 
# save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
# remove(bb_all_three)
```

## Load temp files if we are skipping steps above run if we are skipping steps above
```{r eval=FALSE}
## For cropped detections, need..
# 1. full set of detections (d_all from above)
load(file='../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')

@@

### Make cropped detections for Y/SA, join, make cropped large data
```{r}
detections_cropped_Y <- d_y %>%
  filter(person==0) %>% #only get frames where detections so comparable
  filter((height<(.6*480))) %>%  ## 
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

@@

## Make cropped detections in top 60% of frame for S,A
detections_cropped_SA <- bb_SA %>%
  filter(height<(.6)) %>%  ## 
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))  
# join all together
all_cropped_detections <- detections_cropped_SA %>%
  ungroup() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  full_join(detections_cropped_Y)

@@

>>>>

## Load, process, merge Y's data
### Now load in bounding box data from Y, which has detection rates built in
```{r}
load('../data/raw_data/Y_bounding_boxes.RData') #df again as import
y_data <- df %>%
  rowwise() %>%
  mutate(age = str_split_fixed(vid_name, '_',4)[,3])
remove(df)

@@

## frame
height_px = 480; width_px = 640
bb_all_three <- d_y %>%
  filter(person==0) %>% # only rows with detections for now so comparable to bb_all
  # mutate(left = left*width_px, top = top*height_px, height = height*height_px, width = width*width_px) %>% #unnormalize data so comparable
  full_join(bb_SA) %>% # join with SA bounding boxes
  mutate(center_x = left + width/2, center_y = top - height/2, area = width*height)

save(bb_all_three, file = '../data/all_bounding_boxes_three_kids_preprocessed.RData')
remove(bb_all_three)
```

# Load temp files if we are skipping steps above run if we are skipping steps above
```{r eval=FALSE}
## For cropped detections, need..
# 1. full set of detections (d_all from above)
load(file='../data/preprocessed_data/openpose_detections_filtered_2020-01-29.RData')

@@

### Make cropped detections for Y/SA, join, make cropped large data
```{r}
detections_cropped_Y <- d_y %>%
  filter(person>0) %>% #only get frames where detections so comparable
  mutate(top_real = top - height) %>% ## TOP IS ACTULALY BOTTOM AND 0,0 IS in the "TOP/LEFT" ! OMG.
  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
  filter(center_y<(.6*480)) %>%  ## 
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

@@

## Make cropped detections in top 60% of frame for S,A
detections_cropped_SA <- bb_SA %>%
  mutate(top_real = top - height) %>% ## TOP IS ACTULALY BOTTOM AND 0,0 IS TOP
  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
  filter(center_y<(.6)) %>%  ## 
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

# join all together
all_cropped_detections <- detections_cropped_SA %>%
  ungroup() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  full_join(detections_cropped_Y)

@@

### Make center detections for Y/SA, join, make centered large data
```{r}
limit_lower =.2
limit_upper =.8
y_max = 480
x_max = 640

detections_center_Y <- d_y %>%
  filter(person>0) %>% #only get frames where detections so comparable
  mutate(top_real = top - height) %>%
  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
  filter(center_y<(limit_upper*y_max) & center_x<(limit_upper*x_max) & center_y>(limit_lower*y_max) & center_x>(limit_lower*x_max)) %>%  ## 
  group_by(vid_name, frame, child_id, age_days) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))

detections_center_Y <- detections_center_Y %>%
 ungroup() %>%
 mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id))

## Make center detections in top 60% of frame for S,A
detections_center_SA <- bb_SA %>%
  mutate(top_real = top - height) %>%
  mutate(center_y = top_real + height/2, center_x = left + width/2) %>%
  filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%  ## 
  group_by(vid_name, frame, child_id) %>%
  summarize(hand_detected = (sum(label=="hand")>0), face_detected = (sum(label=="face")>0), num_hands = sum(label=="hand"), num_faces = sum(label=="face"), num_people = sum(label=="pose"))  
# join all together
all_center_detections <- detections_center_SA %>%
  ungroup() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  full_join(detections_center_Y)
```

## Join back with big data structure
```{r}
## clean up workspace or else we run into memory limits
# center detections
remove(detections_center_Y)
remove(detections_center_SA)

# # bb data
# remove(y_data)
# remove(bb_all)

## need to get "FALSE" on frames where we didn't have info to be able to compute proportions; uses d_all from earlier and fills it all back in
all_center_detections <- all_center_detections %>%
  select(-age_days, -child_id) %>%
  mutate(face_openpose_center = face_detected, hand_openpose_center = hand_detected)

d_center <- d_all %>% ## needs to be loaded!
  as_tibble() %>%
  mutate(vid_name = as.factor(vid_name), child_id = as.factor(child_id)) %>%
  select(vid_name, frame, child_id, age_days, face_openpose, hand_openpose) %>%
  left_join(all_center_detections, by=c("vid_name","frame"))

if (saveFiles){
save(d_center, file = paste0('../data/preprocessed_data/openpose_detections_filtered_center2', today(), '.RData'))
}
```

### 2021-04-16 preprocessing/_old/4_preprocess_datasets_per_vid.Rmd
reorganize preprocessing folder -- port old scripts to old folder

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(lubridate)
library(egg)
theme_set(theme_few())
## are we saving outputs
saveFiles = TRUE
```

>>>>

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(lubridate)
library(egg)
library(here)
theme_set(theme_few())
## are we saving outputs
saveFiles = TRUE
```

```{r}
op_file_dir = "../data/op_outputs_per_vid/"
op_files = dir(op_file_dir)

```{r}
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

   if (vid_index == 1 ){
     all_vid_data <- summary_vid_data
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(summary_vid_data)
   }
}
```

```{r}

### 2021-04-16 preprocessing/_old/4_preprocess_datasets_per_vid_2.Rmd
reorganize preprocessing folder -- port old scripts to old folder

---
title: "SAYCAM Main analyses from bounding box outputs"
author: "Bria Long"
date: "6/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```
## OP bounding box outputs
```{r}
op_file_dir = here("/data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
```

## Read in bounding box outputs from each vid, summarize and compile.
```{r}
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected), num_detect = length(hand_detected))

@@

## Data cleaning
### Choose bins across which to analyze data
```{r}
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)
```

### Regualrize vid names
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

### Load list of videos we should exclude -- allocentric videos
```{r}
allocentric_file = here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

### Get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name)
```

### Some videos still need metadata (!)
```{r}
missing_age <-all_vid_data %>%
  filter(is.na(age_days))
```

>>>>

---
title: "saycam bb outputs compile"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(lubridate)
library(egg)
library(here)
theme_set(theme_few())
## are we saving outputs
saveFiles = TRUE
```

```{r}
op_file_dir = "../data/op_outputs_per_vid/"
op_files = dir(op_file_dir)

```

```{r}
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(prop_hands = mean(hand_detected), prop_faces = mean(face_detected), num_detect = length(hand_detected))

@@
